\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2025-02-22 Manuscript/reply2.tex
Wrote replies to comments, needs to be revised

The manuscript has been revised accordingly with the following most
notable changes:
\begin{enumerate}
\item
  The focus of the study has been clarified in the completely
  rewritten introduction. The two objectives are 1) to investigate
  whether the reaction times at the 2022 World Championships were
  significantly different from the other competitions; and 2) to
  assess the appropriateness of the 0.1-second threshold.
\item
  Additional data

@@

We thank the reviewer for the accurate summary of our contributions

@@

@@

@@

@@

>>>>

The manuscript has been revised accordingly with the following most
notable changes:
\begin{enumerate}
\item
  The manuscript has been re-structured to have 4 sections: introduction,
  analysis of 2022 times, analysis of a proper reaction barrier, and discussion.
  Within the second and third sections there are data, methods, and results
  subsections.
\item
  General revisions of tidying the manuscript.

@@

We thank the reviewer for the accurate summary of our contributions and
understand there are some smaller issues to still address.

@@

We understand there were issues about distinguishing between the datasets being
used for each section.  After re-grouping the paper, each problem's data, 
methods, and results section are consecutive, leading to increased reader
comprehension.  The dataset describing the 2022 analysis is found in
the last paragraph of page 5 and the dataset describing the RT barrier analysis
is found in the first paragraph of section 3.1

@@

The manuscript has been revised again and the langugage in Table 1 is now
consistent.  The Table 2 nomenclature is now easier to interpret because the
methods section describing the symbols is now placed on the page before.

@@

We have added additional explanations in the discussion section to address both
seasonality and age, although we don't think either one will be largely
impactful.  By including times from athletes in both 2019 and 2022, there are
athletes who got older from 2019 to 2022 but athletes in 2022 will be younger
than they were in 2023.  Including both comparisons is meaningful as it helps
diminish this effect.  Likewise while seasonality may impact the 2022 national
level comparison, the 2019 and 2023 comparisons mitigate this factor.

@@

Thank you for your comments.
